Automatic Summarization of Scientific Texts

### 2018-06-10 paper/paper.tex
Add seq2seq output example

>>>>

After some training our model was able to generate meaningful titles for most abstracts. Take a look at this example:

\paragraph{Abstract} this is great popcorn and i too have the whirly pop. the unk packs work wonderfully. i have not found it too salty or the packages leak. i have found the recent price of \$35 too expensive and have purchased direct from great american for half the price.

\paragraph{Predicted summary} great popcorn!!

\paragraph{Actual summary} great unk american popcorn
